Understanding \& Developing Artificial Neural Networks

### 2017-03-08 research paper/paper.tex
Paper updated, docs added.

There are limitations to this method. First of all, what if we are stuck
in a local minimum, our goal is to find the global minimum for the cost
function. In another word, this method will not work properly for a non-convex
function.

@@

\emph{Phase 1: Propagation: Each propagation
includes forward and backward propagation:}
\footnote{The steps are referenced from
Wikipedia who referenced:
\href{http://numericinsight.com/uploads/A_Gentle_Introduction_to_Backpropagation.pdf}{A
Gentle Introduction to Backpropagation - An intuitive tutorial by
Shashi Sathyanarayana}~The article contains pseudocode ("Training
Wheels for Training Neural Networks") for implementing the algorithm.}

@@

\begin{equation} \tag{BP2}
	{\delta}^{l} = (\left( w^{l + 1} \right)^{T}\delta^{l + 1})\bigodot\sigma'(z^{l})\
\end{equation}

In the equation above, \(\left( w^{l + 1} \right)^{T}\) is the transpose of the weight
matrix \(\left( w^{l + 1} \right)\) for the
\emph{(l+1)\textsuperscript{th}} layer. We can calculate the error
\(\delta^{l + 1}\) at the \emph{(l+1)\textsuperscript{th }}layer by using (BP1). When
the transpose weight matrix is applied \(\left( w^{l + 1} \right)^{T}\),
we can think of this as moving the error backward through the network,
giving us some sort of measure of the error at the output of the
l\textsuperscript{th} layer. Finally, we take the Hadamard
product\(\ \bigodot\sigma'(z^{l})\).

Micheal Nilsson praises the power of (BP1) and (BP2): "By combining (BP1) with (BP2), the error \(\delta^{l}\) for any
layer in the network can by computed." We start by using~(BP1)~to
compute~\(\delta^{l}\), then apply Equation~(BP2)~to
compute~\(\delta^{L - 1}\), then Equation~(BP2)~again to
compute~\(\delta^{L - 2}\), and so on, all the way back through the
network. In the subsection below, there will be an example of using (BP1) with (BP2) in a simple three layer neural network.

@@

@@

@@

Calculate the \(\delta\) for the third layer of the network.
\[\frac{\partial J}{\partial w_{(2)}} = {{(a}^{(2)})}^{T}\delta_{(3)}\]

Use the calculated result to help us modify the second layer of weights
in the network.
\[\delta_{(2)} = \delta_{\left( 3 \right)}\left( w_{\left( 2 \right)} \right)^{T}\sigma'(z_{(2)})\]

Calculate the \(\delta\) for the second layer of the network.
\[\frac{\partial J}{\partial w_{(1)}} = \ x^{T}\delta_{(2)}\]

@@

Here is a visualization of how individual output node is approaching the desired output.

\centerline{\includegraphics[width=1\linewidth]{graph1} }
\centerline{Figure 7}
\vspace{0.5cm}

Line 0-3 are lowering as we train the network. Line 4, is approaching 1 as we keep train the network. This figure displayed that the error of the network \(C\) is being minimized.

Here is a graph of the correction of the neural network over times of training. Each time the network will train with 1000 out of 60,000 training data. After, The program will shuffle the training data and repeat the training process for 197 times, or until the network reaches 95\% accuracy.

>>>>

There are limitations to this method. First of all, what if we are stuck
in a local minimum? Our goal is to find the global minimum for the cost
function. In another word, this method will not work properly for a non-convex
function.

@@

\emph{Phase 1: Propagation: Each propagation
includes forward and backward propagation:}
\footnote{\href{http://numericinsight.com/uploads/A_Gentle_Introduction_to_Backpropagation.pdf}{A Gentle Introduction to Backpropagation - An intuitive tutorial by
Shashi Sathyanarayana}~The article contains pseudocode ("Training
Wheels for Training Neural Networks") for implementing the algorithm.}

@@

\begin{equation} \tag{BP2}
	{\delta}^{l} = (\left( w_{(l + 1)} \right)^{T}\delta_{(l + 1)})\odot\sigma'(z_{(l)})\
\end{equation}

In the equation above, \(\left( w_{(l + 1)} \right)^{T}\) is the transpose of the weight
matrix \(\left( w_{(l + 1)} \right)\) for the
\emph{(l+1)\textsuperscript{th}} layer. When
the transpose weight matrix is applied, this can be seem as moving the error backward through the network,
giving us some sort of measure of the error at the output of the
l\textsuperscript{th} layer. Finally, we take the Hadamard
product \footnote{https://en.wikipedia.org/wiki/Hadamard\_product\_(matrices)} \(\ \odot\sigma'(z^{l})\).

Equation (5) above can help us calculate (BP2), which is matrix based. Hadamard product can be understood as: 
\[
\begin{bmatrix}
	a_1 & b_1 \\
	c_1 & d_1
\end{bmatrix}
\odot
\begin{bmatrix}
	a_2 & b_2 \\
	c_2 & d_2
\end{bmatrix}
= 
\begin{bmatrix}
	a_1 * a_2 & b_1 * b_2 \\
	c_1 * c_2 & d_1 * d_2
\end{bmatrix}
\]

The incredible power of the equation above becomes apparent when (BP1) and (BP2) are working together. We start by using~(BP1)~to
compute~\(\delta^{l}\), then apply Equation~(BP2)~to
compute~\(\delta^{L - 1}\), then Equation~(BP2)~again to
compute~\(\delta^{L - 2}\), and so on, all the way back through the
network. In the subsection below, there will be an example of using (BP1) with (BP2) in a simple three layer neural network.

@@

Bias nodes are not necessary in neural networks. However, they are helpful in improving the network's learning. In a linear function, \(y = mx + b\), the b term will effect the vertical shift of the function. Bias nodes for neural networks behaves similarly. It can translate the sigmoid function on the coordinate plane. \footnote{Make Your Own Neural Network -- Tariq Rashid}

@@

In equation (6), \(a_{in}\) is the output with weights \(w\). And \(delta_{out}\) is the error of the neural output from the weight w.

\centerline{\includegraphics[width=0.6\linewidth]{bp4} }
%\centerline{Figure 5}
\vspace{0.5cm}

@@

Calculate the \(\delta\) for the third layer of the network. This looks quite similar to Equation (6).
\[\frac{\partial C}{\partial w_{(2)}} = {{(a}_{(2)})}^{T}\delta_{(3)}\]

The equation yields the partial derivative of C in terms of second layer weights \(w_{(2)}\), which connect the hidden layer to the output layer. Transposing the hidden layer output, \(a_{(2)}\) and multiplying \(\delta_{(3)}\) we can calculate the rate of change, which will be applied to \(w_{(2)}\)
\[\delta_{(2)} = \delta_{\left( 3 \right)}\left( w_{\left( 2 \right)} \right)^{T}\sigma'(z_{(2)})\]

Calculate the \(\delta\) for the second layer of the network.
\[\frac{\partial C}{\partial w_{(1)}} = \ x^{T}\delta_{(2)}\]

@@

Here is a visualization of the change in weight effect the cost of output nodes. Line 0-3 are lowering as we train the network. This figure displayed that the error of the network \(C\) is being minimized.

\centerline{\includegraphics[width=1\linewidth]{graph1} }
\centerline{Figure 7}
\vspace{0.5cm}
Here is a graph of the correction of the neural network over times of training. Each time the network will train with 1000 out of 60,000 training data. After, The program will shuffle the training data and repeat the training process for 197 times, or until the network reaches 95\% accuracy.
